Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-05 snTomas.tex
test

To refine the redshift and phase constraints on \tomas, we next fit
the spectrum with a custom spectral matching program that employs a
library of Type Ia SN SEDs.  This library is similar to the Type Ia
spectral set used by SNID, but also includes more recent SNe with
well-observed spectral time series that extend to rest-frame UV
wavelengths (e.g. SN 2011fe and 2014J).  We first use an approach
similar to the SNID algorithm: warping the pseudo-continuum of each
template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
match the observed SED of SN \tomas.  From this analysis we find
results that are consistent with the SNID fits: a redshift of
$z=1.31\pm0.01$ and a phase of $0\pm3$ rest-frame days. The
best-fitting spectral template is the normal Type Ia SN 2012cg, shown
in the bottom panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
per degree of freedom $\nu$ equal to 42.1/87.

>>>>

To refine the redshift and phase constraints on \tomas, we next fit
the spectrum with a custom spectral matching program that employs a
library of Type Ia SN SEDs.  This library is similar to the Type Ia
spectral set used by SNID, but also includes more recent SNe with
well-observed spectral time series that extend to rest-frame UV
wavelengths (e.g. SN 2011fe and 2014J).  We first use an approach
similar to the SNID algorithm: warping the pseudo-continuum of each
template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
match the observed SED of SN \tomas.  From this analysis we find
results that are consistent with the SNID fits: a redshift of
$z=1.31\pm0.01$ and a phase of $0\pm3$ rest-frame days. The
best-fitting spectral template is the normal Type Ia SN 2012cg, shown
in the top panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
per degree of freedom $\nu$ equal to 42.1/87.
